\textbf{Modelling Neuroplasticity: Using Machine Learning to Learn About TMS Data}

### 2023-06-15 paper/paper.tex
.

    Let $x \in \textbf{x}$ be the evoked potential of a single paired
    stimulation. Then we define two pulse-specific relative amplitude measures,
    $\rho : \mathbb{R} \to \mathbb{R}, \delta : \mathbb{R} \to \mathbb{R}$,
    where

    \begin{equation} 
        \rho(x) := \frac{mx}{\sum_{i=1}^mt_j}
    \end{equation}

    \begin{equation} 
        \delta(x) := \frac{x}{m}\sum_{j=1}^m\frac{1}{t_j} 
    \end{equation}
\end{definition}

\begin{theorem} 
    $\forall x: x \in \mathbb{R}^+:\delta(x) \geq \rho(x)$. (For a proof of this
    property, consult the appendix.) 
\end{theorem}

Notice that $\rho(x)$ is the proportion between the potential $x$, evoked by a
paired stimulation, with respect to the average potential of single test
stimulations. On the other hand, $\delta(x)$ is the average proportion of $x$
with respect to each single test pulse.

@@

    \begin{align*}
        \pi = \frac{\rho(x_1) + \ldots + \rho(x_n)}{n}
    .\end{align*}

@@

>>>>

    Let $x \in \mathbb{R}^+$ be the evoked potential of a single paired
    stimulation, and $\textbf{t} \in \mathbb{R}^m$. Then we define two
    pulse-specific relative amplitude measures, $\rho : \mathbb{R} \times
    \mathbb{R}^m \to
    \mathbb{R}, \delta : \mathbb{R}\times \mathbb{R}^m \to \mathbb{R}$, where

    \begin{equation} 
        \rho(x, \textbf{t}) := \frac{mx}{\sum_{i=1}^mt_j}
    \end{equation}

    \begin{equation} 
        \delta(x, \textbf{t}) := \frac{x}{m}\sum_{j=1}^m\frac{1}{t_j} 
    \end{equation}
\end{definition}

\begin{theorem} 
    $\forall x: x \in \mathbb{R}^+:\delta(x, \textbf{t}) \geq \rho(x,
    \textbf{t})$. (For a proof of this property, consult the appendix.) 
\end{theorem}

The function $\rho$ represents the proportion between a potential $x$, evoked by
a paired stimulation, with respect to the average potential of single test
stimulations. On the other hand, $\delta$ is the average proportion of $x$
with respect to each single test pulse.

@@

    \begin{align*}
        \pi = \frac{\rho(x_1, \textbf{t}) + \ldots + \rho(x_n, \textbf{t})}{n}
    .\end{align*}

@@

\begin{remark}
    Observe that 
    \begin{align*}
        \frac{\partial \rho}{\partial x } &= \frac{m}{\sum_{i = 1}^m
        t_j} \\ \frac{\partial \rho}{\partial t_i} &= -\frac{xm}{\big( \sum_{j =
        1}^m t_j \big)^2} \\ 
                    \frac{\partial \delta}{\partial x} &= \frac{1}{m}\sum_{i =
                    1}^m t_i \\ 
                        \frac{\partial \delta}{\partial t_i} &= -\frac{x}{mt_i^2}
    \end{align*}
\end{remark}

Since $\textbf{t}$ remains constant in the computation of the different relative
amplitudes of $\textbf{x}_1, \ldots, \textbf{x}_n$, we shall use from now
onwards the notation $\rho(x), \delta(x)$ to denote $\rho(x, \textbf{t})$ and
$\delta(x, \textbf{t})$, respectively.
